% !TEX root = /Users/us2009801/Documents/GitHub/ProofsAndProblemSolving/main.tex
\chapter{Homework 1 - Saturday, November 3\ts{rd}, 2018}
\section{\S 1 Differential Equations}
\begin{prob}
Analyze the logical forms of the following statements. Use A to represent "Alice has a dog," B to represent "Bob has a dog," and C to represent "Carol has a cat" to write each as a symbolic statement.
\begin{enumerate}
\item Either Alice or Bob has a dog.\\
$A \vee B $
\item Neither Alice nor Bob has a dog, but Carol has a cat.\\
$ \neg (A \wedge B) \wedge C $
\item Either Alice has a dog and Carol has a cat, or Bob has a dog and Carol does not have a cat.\\
$ (A \wedge C) \vee (B \wedge \neg C) $
\end{enumerate}
This is similar to Example 1.1.2 and to Exercise 2 in Section 1.1 of your SNHU MAT299 textbook.
\end{prob}
\begin{prob}
If D stands for "Doug is tall" and E stands for "Edie is short," what English sentences are represented by the following expressions?
\begin{enumerate}
\item $(D \wedge E) \vee \neg D$\\
Either Doug is tall and Edie is short, or Doug is not tall
\item $(D \vee \neg E) \wedge \neg(D \wedge E)$\\
Either Doug is tall or Edie is not short and both Doug is not tall and Edie is not short
\item $\neg D \wedge ((E \wedge D) \vee \neg E )$\\
Doug is not tall and either Edie is short and Doug is tall, or Eddie is not short
\end{enumerate}
This is similar to Example 1.1.3 and to Exercise 6 in Section 1.1 of your SNHU MAT299 textbook.
\end{prob}
\begin{prob}
Make a truth table for the following formula.
$$ (G \vee \neg H) \wedge \neg(G \wedge L) $$
This is similar to Example 1.2.2 and to Exercise 2 in Section 1.2 of your SNHU MAT299 textbook.
\begin{center}
 \begin{tabular}{|c|c|c|c|c|c|c|c|} 
 \hline
 G & H & L & $\neg H$ & $G \vee \neg H$ & $G \wedge L$ & $\neg G \wedge L$ & $ (G \vee \neg H) \wedge \neg(G \wedge L) $ \\ 
 \hline
T & T & T & F & T & T & F & F\\
T & T & F & F & T & F & T & T\\
T & F & T & T & T & T & F & F\\
T & F & F & T & T & F & T & T\\
F & T & T & F & F & F & T & F\\
F & T & F & F & F & F & T & F\\
F & F & T & T & T & F & T & T\\
F & F & F & T & T & F & T & T\\
 \hline
\end{tabular}
\end{center}
\end{prob}
\begin{prob}
Use truth tables to determine which of the following formulas are equivalent to each other.
\begin{enumerate}
\item (J ? K) ? (¬J ? ¬K)
\item J ? K
\item J ? ¬K
\item ¬(¬J ? K)
\item (J ? ¬K) ? K
\end{enumerate}
This is similar to Example 1.2.4 and to Exercise 8 in Section 1.2 of your SNHU MAT299 textbook.
\end{prob}


$\vee$ Or Vee\\
$\wedge$ and Wedge\\
$\neg \cup \vee \wedge$


















































